%-------------------------
% Resume in LaTeX
% Author: Israel Alcantara
% Based off of: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Israel Alcántara} \\ \vspace{1pt}
    \small 201-744-7377 $|$ 
    \href{mailto:iaa48@njit.edu}{\underline{iaa48@njit.edu}} $|$ 
    \href{https://linkedin.com/in/israel-alcantara}{\underline{linkedin.com/in/israel-alcantara}} $|$
    \href{https://github.com/iaalcantara17}{\underline{github.com/iaalcantara17}} $|$
    \href{https://israelalcantara.vercel.app/}{\underline{israelalcantara.vercel.app}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {New Jersey Institute of Technology – Ying Wu College of Computing}{Newark, NJ}
      {Bachelor of Science in Computer Science $|$ GPA: 3.505}{May 2026}
      \begin{flushleft}
        \small \textbf{Relevant Coursework}: Data Structures \& Algorithms $|$ Programming Language Concepts $|$ Information Design Techniques $|$ Designing the User Experience $|$ Foundation of Computer Science I $|$ Intensive Programming in Linux $|$ Introduction to Data Science $|$ Database System Design \& Management $|$ Principles of Operating Systems $|$ Introduction to Computer Networks $|$ Probability \& Statistics
      \end{flushleft}
  \resumeSubHeadingListEnd

%-----------KEY SKILLS-----------
\section{Key Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Programming Languages}{: Python, Java, C/C++, Bash Script, HTML, JavaScript, CSS, SQL} \\
      \textbf{Frameworks \& Tools}{: Linux, Git, Google Colab, VS Code, Vim, IntelliJ, Eclipse, Node.js, MySQL, MongoDB, LaTeX} \\
      \textbf{Libraries}{: Pandas, NumPy, Matplotlib, Scikit-learn, Plotly, Dash, Seaborn} \\
      \textbf{Languages}{: Fluent in English and Spanish} \\
    }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Office Assistant}{Sept. 2024 -- Present}
      {Educational Opportunity Program (EOP) - NJIT}{Newark, NJ}
      \resumeItemListStart
        \resumeItem{Spearheaded office operations and student engagement by efficiently managing front desk activities, coordinating over 15 appointments weekly using a scheduling website, and ensuring accurate and confidential record-keeping.}
        \resumeItem{Streamlined document preparation and data entry workflows in Microsoft Excel, reducing administrative workload by 30\% and improving office organization for faster document retrieval.}
      \resumeItemListEnd

    \resumeSubheading
      {Delivery Technician/Lab Technician}{Sept. 2022 -- Present}
      {Media and Technology Support Services (MTSS) - NJIT}{Newark, NJ}
      \resumeItemListStart
        \resumeItem{Collaborated with a team of five to standardize audiovisual equipment setup procedures and implement routine maintenance protocols, boosting equipment reliability by 40\% across more than 100 lectures annually.}
        \resumeItem{Diagnosed and resolved technical issues in classrooms and labs, utilizing systematic troubleshooting techniques to identify problems and implement solutions, leading to a 30\% reduction in equipment downtime.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Event Coordination Director}{May 2024 -- May 2025}
      {Society of Hispanic Professional Engineers (SHPE) - NJIT}{Newark, NJ}
      \resumeItemListStart
        \resumeItem{Organized and executed 12+ networking and professional development events using Google Sheets and the school's volunteer coordination platforms, increasing participation by 50\% and reducing planning time by 20\%.}
        \resumeItem{Created strategic event calendars and managed volunteer teams of approx. 10 people to execute events efficiently, resulting in a 20\% reduction in planning time and increased attendee satisfaction.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Data Analysis and Prediction App} $|$ \emph{Streamlit, Python, Scikit-learn} $|$ Jupyter Notebook} {Nov. 2024 – Dec. 2024}
          \resumeItemListStart
            \resumeItem{Developed an interactive web app for CSV data upload, visualization, and machine learning model training using a Gradient Boosting Regressor, featuring dynamic charts for real-time insights.}
            \resumeItem{Built automated data preprocessing that handles missing values, scales numerical data, and encodes categories, allowing users to select features and evaluate model predictions in real time.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Compiler for SFort95 Language} $|$ \emph{Visual Studio Code, Git} $|$ C++} {March 2024 – April 2024}
          \resumeItemListStart
            \resumeItem{Developed a full SFort95 compiler with lexical analysis, recursive-descent parsing, and interpretation, ensuring compliance with Fortran95 standards and robust syntax validation.}
            \resumeItem{Designed and implemented a state-based lexical analyzer, operator-precedence parsing, and runtime checks, generating token reports and handling errors like undefined variables and division by zero.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}