%-------------------------
% Resume in Latex
% Author: Israel Alcantara
% Based off of: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Israel Alcántara} \\ \vspace{1pt}
    \small 201-744-7377 $|$ 
    \href{iaa48@njit.edu}{\underline{iaa48@njit.edu}} $|$ 
    \href{https://linkedin.com/in/israel-alcantara}{\underline{www.linkedin.com/in/israel-alcantara}} $|$
    \href{https://github.com/iaalcantara17}{\underline{github.com/iaalcantara17} 
    $|$
    \href{https://iaalcantara17.github.io/portfolio-website/}{\underline{https://iaalcantara17.github.io/portfolio-website/}}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {New Jersey Institute of Technology}{Newark, NJ}
      {Bachelor of Science in Computer Science $|$ GPA: 3.425}{May 2026}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Office Assistant}{Sept. 2024 -- Present}
      {Educational Opportunity Program (EOP)}{Newark, NJ}
      \resumeItemListStart
        \resumeItem{Enhanced office operations and student engagement by efficiently managing front desk activities, coordinating over 15 appointments weekly using a scheduling website, and ensuring accurate and confidential record-keeping.}
        \resumeItem{Streamlined document preparation, data entry, and office organization using Microsoft Office, boosting operational efficiency by at least 30\%.}
        
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Delivery Technician/Lab Technician}{Sept. 2022 -- Present}
      {Media and Technology Support Services (MTSS)}{Newark, NJ}
      \resumeItemListStart
        \resumeItem{Collaborated with a team of five to standardize audiovisual equipment setups and implement routine maintenance protocols, boosting reliability by 40\% across more than 100 lectures annually.}
        \resumeItem{Effectively diagnosed and resolved technical issues in classrooms and labs, utilizing systematic troubleshooting techniques to identify problems and implement solutions, leading to a 30\% reduction in equipment downtime.}
    \resumeItemListEnd

\resumeSubheading
      {Event Coordination Director}{Sept. 2024 -- Present}
      {Society of Hispanic Professional Engineers (SHPE)}{Newark, NJ}
      \resumeItemListStart
        \resumeItem{Led the planning and execution of 12+ networking and professional development events using Google Sheets and volunteer coordination websites and forms, increasing participation by 50\% and reducing planning time by 20\%.}
        \resumeItem{Developed strategic event calendars and managed volunteer teams to execute events efficiently, resulting in a 20\% reduction in planning time and increased attendee satisfaction.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Lexical Analyzer for SFort95 Language} $|$ \emph{Visual Studio Code, Git} $|$ \textbf{C++}} {March 2024}
          \resumeItemListStart
            \resumeItem{Implemented state-based transitions to recognize multi-character tokens like identifiers and constants.}
            \resumeItem{Error detection and reporting for unrecognized lexemes using error states.}
            \resumeItem{Supported various language-specific constructs such as comments and string literals}
            \resumeItem{Produced detailed token reports including frequency and types of tokens identified.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Recursive-Descent Parser for SFort95 Language} $|$ \emph{Visual Studio Code, Git} $|$ \textbf{C++}}{April 2024}
          \resumeItemListStart
            \resumeItem{Implemented functions for each syntactic rule, supporting constructs like variable declarations, assignment statements, and control structures (IF, PRINT).}
            \resumeItem{Managed error reporting with descriptive messages for common syntax errors such as missing semicolons or undefined variables.}
            \resumeItem{Integrated operator precedence handling, including unary and binary operations with correct associativity rules.}
            \resumeItem{Parsed and validated expressions, ensuring type compatibility between operands.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Interpreter for SFort95 Language} $|$ \emph{Visual Studio Code, Git} $|$ \textbf{C++}}{April 2024}
          \resumeItemListStart
            \resumeItem{Built a symbol table to track variable types and values, ensuring correct type conversions and assignments.}
            \resumeItem{Evaluated arithmetic and relational expressions, applying precedence and associativity rules.}
            \resumeItem{Implemented run-time checks for error handling, including division by zero and type mismatches.}
            \resumeItem{Managed control flow with support for conditional statements and block execution.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Key Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Relevant Coursework}{: Roadmap to Computing $|$  Intro to Computer Science I $|$ Data Structures \& Algorithms in Java $|$ Programming Language Concepts $|$ Information Design Techniques $|$ Foundation of Computer Science I $|$ Intensive Programming in Linux $|$ Introduction to Data Science $|$ Probability \& Statistics} \\
     \textbf{Programming Languages}{: Python, Java, C/C++, C\#, Bash, HTML, JavaScript, CSS} \\
     \textbf{Developer Tools}{: Git, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib}\\
     \textbf{Languages}{: Fluent in English and Spanish} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
